---
title: "CW01b"
author: "Ralph_Huang"
date: "2020/8/21"
output: redoc::redoc
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## The rest of packages for CW01

Well, in order to finish the homework in time, I have to find some easy packages. 

### jsonlite

This is a important and extremely easy package to turn json file into data frame.
```{r jsonlite}
library(jsonlite)
json <- 
'[
  {"Name" : "Mario", "Age" : 32, "Occupation" : "Plumber"},
  {"Name" : "Peach", "Age" : 21, "Occupation" : "Princess"}
]'
mydf <- fromJSON(json)
mydf
```

### utf-8

UTF-8 is the most widely used encoding nowadays. It would be confulsed when encoding goes wrong.

```{r utf-8}
#install.packages("utf8")
library(utf8)
x <- c("fa\u00E7ile", "fa\xE7ile", "fa\xC3\xA7ile")
Encoding(x) <- c("UTF-8", "latin1", "bytes")
as_utf8(x) 
utf8_normalize("ð–¸ð—ˆ ð”ð§ð¢ðœð¨ððž ð—… ð—ð–¾ð—‹ð–½ ð•Œ ð—…ð—‚ð—„ð–¾ ð‘¡ð‘¦ð‘ð‘’ð‘“ð‘Žð‘ð‘’ð‘  ð—Œð—ˆ ð—ð–¾ ð—‰ð—Žð— ð—Œð—ˆð—†ð–¾ ðšŒðš˜ðšðšŽðš™ðš˜ðš’ðš—ðšðšœ ð—‚ð—‡ ð—’ð—ˆð—Žð—‹ ð”–ð”²ð”­ð”­ð”©ð”¢ð”ªð”¢ð”«ð”±ð”žð”¯ð”¶ ð”šð”²ð”©ð”±ð”¦ð”©ð”¦ð”«ð”¤ð”³ð”žð”© ð”“ð”©ð”žð”«ð”¢ ð—Œð—ˆ ð—’ð—ˆð—Ž ð–¼ð–ºð—‡ ð“®ð“·ð“¬ð“¸ð“­ð“® ð•—ð• ð•Ÿð•¥ð•¤ ð—‚ð—‡ ð—’ð—ˆð—Žð—‹ ð’‡ð’ð’ð’•ð’”.",
               map_compat = TRUE)
print(intToUtf8(0x1F600 + 0:79))
```
### showtext

The default font is too normal to make the whole picture shiny. Merely changing the font can beautify the plot a lot.

```{r sharefont, echo=FALSE}
#install.packages("showtext")
library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Gochi Hand", "gochi")
font_add_google("Schoolbell", "bell")
font_add_google("Covered By Your Grace", "grace")
font_add_google("Rock Salt", "rock")

## Automatically use showtext to render text for future devices
showtext_auto()

## Tell showtext the resolution of the device,
## only needed for bitmap graphics. Default is 96
showtext_opts(dpi = 96)

set.seed(123)
x = rnorm(10)
y = 1 + x + rnorm(10, sd = 0.2)
y[1] = 5
mod = lm(y ~ x)

op = par(cex.lab = 2, cex.axis = 1.5, cex.main = 2)
plot(x, y, pch = 16, col = "steelblue",
     xlab = "X variable", ylab = "Y variable", family = "gochi")
grid()
title("Draw Plots Before You Fit A Regression", family = "bell")
text(-0.5, 4.5, "This is the outlier", cex = 2, col = "steelblue",
     family = "grace")
abline(coef(mod))
abline(1, 1, col = "red")
par(family = "rock")
text(1, 1, expression(paste("True model: ", y == x + 1)),
     cex = 1.5, col = "red", srt = 20)
text(0, 2, expression(paste("OLS: ", hat(y) == 0.79 * x + 1.49)),
     cex = 1.5, srt = 15)
legend("topright", legend = c("Truth", "OLS"), col = c("red", "black"), lty = 1)

par(op)

```

### redoc




```{r pressure, echo=FALSE}
#remotes::install_github("noamross/redoc")
library(redoc)
#just set output as `redoc::redoc`

#dedoc(docx = "CW01b.docx")

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
