---
title: "CW05"
author: "Ralph_Huang"
date: "2020/9/9"
output:
  html_document: default
  pdf_document: default
  always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Spatial

In this week, we will explore spatial data. I have limited accumulation in this area. It's hard to write a pre-overview before any learning.

### GIS data

#### 5.1 sf

After coping some codes in the orientation page of sf

```{r sf_feature example}
library(sf)
## Linking to GEOS 3.8.0, GDAL 3.0.4, PROJ 7.0.0
nc <- st_read(system.file("shape/nc.shp", package="sf"))
## Reading layer `nc' from data source `/tmp/RtmpNt5oDA/Rinst34af264cc9b4/sf/shape/nc.shp' using driver `ESRI Shapefile'
## Simple feature collection with 100 features and 14 fields
## geometry type:  MULTIPOLYGON
## dimension:      XY
## bbox:           xmin: -84.32385 ymin: 33.88199 xmax: -75.45698 ymax: 36.58965
## geographic CRS: NAD27
class(nc)
attr(nc, "sf_column")
print(nc[9:15], n = 3)
```

```{r basic plot}
library(tidyr)
library(dplyr)
library(ggplot2)
nc = read_sf(system.file("gpkg/nc.gpkg", package="sf"))
nc2 <- nc %>% st_transform(32119) %>% select(SID74, SID79, geom) %>%   gather(VAR, SID, -geom)
ggplot() + geom_sf(data = nc2, aes(fill = SID)) + facet_wrap( ~ VAR, ncol = 1)
```

```{r geometrilize}
nc_geom <- st_geometry(nc)
nc_geom[[1]]
```


```{r combine points}
p <- rbind(c(3.2,4), c(3,4.6), c(3.8,4.4), c(3.5,3.8), c(3.4,3.6), c(3.9,4.5))
(mp <- st_multipoint(p))
s1 <- rbind(c(0,3),c(0,4),c(1,5),c(2,5))
(ls <- st_linestring(s1))
s2 <- rbind(c(0.2,3), c(0.2,4), c(1,4.8), c(2,4.8))
s3 <- rbind(c(0,4.4), c(0.6,5))
(mls <- st_multilinestring(list(s1,s2,s3)))
p1 <- rbind(c(0,0), c(1,0), c(3,2), c(2,4), c(1,4), c(0,0))
p2 <- rbind(c(1,1), c(1,2), c(2,2), c(1,1))
pol <-st_polygon(list(p1,p2))
p3 <- rbind(c(3,0), c(4,0), c(4,1), c(3,1), c(3,0))
p4 <- rbind(c(3.3,0.3), c(3.8,0.3), c(3.8,0.8), c(3.3,0.8), c(3.3,0.3))[5:1,]
p5 <- rbind(c(3,3), c(4,2), c(4,3), c(3,3))
(mpol <- st_multipolygon(list(list(p1,p2), list(p3,p4), list(p5))))

(gc <- st_geometrycollection(list(mp, mpol, ls)))

```
```{r}
(mix <- st_sfc(st_geometrycollection(list(st_point(1:2))),
    st_geometrycollection(list(st_linestring(matrix(1:4,2))))))
```

```{r write spatial data into file}
st_write(nc, "nc.shp")
```

```{r}
nc.web_mercator <- st_transform(nc, 3857)
sel <- c(1,5,14)
geom = st_geometry(nc.web_mercator[sel,])
buf <- st_buffer(geom, dist = 30000)
plot(buf, border = 'red')
plot(geom, add = TRUE)
plot(st_buffer(geom, -5000), add = TRUE, border = 'blue')
```
```{r}
nc <- st_read(system.file("shape/nc.shp", package="sf"),
    agr = c(AREA = "aggregate", PERIMETER = "aggregate", CNTY_ = "identity",
        CNTY_ID = "identity", NAME = "identity", FIPS = "identity", FIPSNO = "identity",
        CRESS_ID = "identity", BIR74 = "aggregate", SID74 = "aggregate", NWBIR74 = "aggregate",
        BIR79 = "aggregate", SID79 = "aggregate", NWBIR79 = "aggregate"))
st_agr(nc)
data(meuse, package = "sp")
meuse_sf <- st_as_sf(meuse, coords = c("x", "y"), crs = 28992, agr = "constant")
st_agr(meuse_sf)
```

```{r}
opar = par(mar=rep(0,4))
plot(meuse_sf)
```

```{r}
b0 = st_polygon(list(rbind(c(-1,-1), c(1,-1), c(1,1), c(-1,1), c(-1,-1))))
b1 = b0 + 2
b2 = b0 + c(-0.2, 2)
x = st_sfc(b0, b1, b2)
a0 = b0 * 0.8
a1 = a0 * 0.5 + c(2, 0.7)
a2 = a0 + 1
a3 = b0 * 0.5 + c(2, -0.5)
y = st_sfc(a0,a1,a2,a3)
plot(x, border = 'red')
plot(y, border = 'green', add = TRUE)
```
```{r}
st_disjoint(x, y)
st_touches(x, y, sparse = FALSE)
st_within(x, y, sparse = FALSE)
st_contains(x, y, sparse = FALSE)
st_overlaps(x, y, sparse = FALSE)
st_equals(x, y, sparse = FALSE)
st_covers(x, y, sparse = FALSE)
st_covered_by(x, y, sparse = FALSE)
st_covered_by(y, y, sparse = FALSE)
st_equals_exact(x, y,0.001, sparse = FALSE)
```

```{r}
par(mfrow=c(2,2), mar = c(0,0,1,0))
plot(x, col = '#ff333388'); 
plot(y, add=TRUE, col='#33ff3388')
title("x: red, y: green")
plot(x, border = 'grey')
plot(st_difference(st_union(x),st_union(y)), col = 'lightblue', add = TRUE)
title("difference(x,y)")
plot(x, border = 'grey')
plot(st_difference(st_union(y),st_union(x)), col = 'lightblue', add = TRUE)
title("difference(y,x)")
plot(x, border = 'grey')
plot(st_sym_difference(st_union(y),st_union(x)), col = 'lightblue', add = TRUE)
title("sym_difference(x,y)")
```
#### 5.2 & 5.3 spdep & rgdal

Since the `spdep` package was created, spatial weights objects have been constructed as lists with three components and a few attributes, in old-style class listw objects. 

`rgdal` implemented changes in the representation of coordinate reference systems (CRS), and of operations on coordinates.
```{r}
library(spdep)
library(rgdal)
if (exists("rgdal_extSoftVersion")) rgdal_extSoftVersion()
```

```{r}
columbus <- readOGR(system.file("shapes/columbus.shp", package="spData")[1])
nb_q <- poly2nb(columbus) #poly2nb function defaulting to the queen criterion - entities are neighbours if they share a boundary point.
col2 <- droplinks(nb_q, 21)
coords <- coordinates(columbus)
plot(nb_q, coords, col="grey")
plot(col2, coords, add=TRUE)
```

```{r symmetric sparse matrices}
library(Matrix)
library(splm)
nb_B <- nb2listw(col2, style="B", zero.policy=TRUE)
B <- as(nb_B, "CsparseMatrix")
all(B == t(B))
nb_B1 <- mat2listw(as(B, "dgTMatrix"))
B
```

PROJ.4. use key-value string. The key-value string is taken as +key=value, where =value could be omitted for some keys, and the definition of each projection is built up from space-separated key-value string, such as +proj=utm +zone=25 +south for Universal Transverse Mercator zone 25 in the southern hemisphere.

```{r}
library(rgdal)
library(sp)
b_pump <- readOGR(system.file("vectors/b_pump.gpkg", package="rgdal"))
proj4string(b_pump)
```

```{r}
if (packageVersion("sp") > "1.4.1") {
  WKT <- wkt(b_pump)
} else {
  WKT <- comment(slot(b_pump, "proj4string"))
}
cat(WKT, "\n")
```

```{r}
set_transform_wkt_comment(TRUE)
is2m <- spTransform(b_pump, CRS(SRS_string="EPSG:4326"))
get_last_coordOp()
```

```{r}
system.time(is1m <- spTransform(b_pump, CRS(SRS_string="EPSG:4326")))
isballpark <- spTransform(b_pump, CRS(SRS_string="EPSG:4326"))
```



### Painting maps

#### 5.4 & 5.5 maps & mapdata

`maps` and `mapdata` include country-wise basic map information.

```{r}
library(maps)
library(mapdata)
map("china", col = "red4", ylim = c(18, 54), panel.first = grid())
title(" 中国地图")
```

#### 5.6 mapview

```{r}
library(mapview)
x <- mapview(is2m, map.type="OpenStreetMap", legend=FALSE) + 
    mapview(is1m, col.regions="green", legend=FALSE) + 
    mapview(isballpark, col.regions="red", legend=FALSE)
x
```

#### 5.7 ggmap & baidumap

```{r}
library(baidumap)
library(ggmap)
options(baidumap.key = 'EOF2QFTXEDoGLasadWUBpqoi')
q = getBaiduMap("中央财经大学",width = 400, height = 400, zoom = 18, scale = 2, messaging = F)
ggmap(q)
```

```{r}
library(magrittr)
library(jsonlite)
getCoordinate("中央财经大学",output = "json") %>% fromJSON()
```

```{r}
getLocation(c(116.3492, 39.96521)) %>% fromJSON()
```

```{r}
getPlace("方老大", "杭州")
```

#### 5.9 REmap

```{r}
library(REmap)
options(remap.ak = "EOF2QFTXEDoGLasadWUBpqoi")
origin = c(rep("上海",4),"柳州", "长沙","南宁")
destination = c("珠海","厦门","北京","柳州","长沙","上海","上海")
dat = data.frame(origin,destination)
out = remap(dat,title = "My route")
out
```

```{r}
library(REmap)
get_geo_position("中央财经大学")
```

```{r}
library(dplyr)
load("C:/Working_files/project-n/dat/202009/byd.RData")
byd = byd %>% mutate(weight = ifelse(dealerType=="4S",2,1)) %>% 
    select(lon, lat, weight) %>%
    apply(2,as.numeric) %>% 
    as.data.frame()
remapH(byd, maptype = "china", minAlpha = 500)
```


