---
title: "CW07"
author: "Ralph"
date: "2020/10/10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Machine Learning

Well, I did overquailfid my self-control that I believe I can learn machine learning during the long holiday automatically.
It is time to pay the debt.

### caret

The `caret` package (short for Classification And REgression Training) contains functions to streamline the model training process for complex regression and classification problems.


```{r caret train}
library(caret)
library(mlbench)
data(Sonar)


inTrain <- createDataPartition(
  y = Sonar$Class,
  ## the outcome data are needed
  p = .75,
  ## The percentage of data in the
  ## training set
  list = FALSE
)

training <- Sonar[ inTrain,]
testing  <- Sonar[-inTrain,]

ctrl <- trainControl(
  method = "repeatedcv", 
  #repeated K-fold cross-validation
  repeats = 3,
  classProbs = TRUE, 
  summaryFunction = twoClassSummary
  #compute measures specific to two-class problems, such as the area under the ROC curve
)

set.seed(123)
plsFit <- train(
  Class ~ .,
  data = training,
  method = "pls", #partial least squares discriminant analysis 
  preProc = c("center", "scale"),
  tuneLength = 15,
  trControl = ctrl,
  metric = "ROC"
)
ggplot(plsFit)
```

```{r caret predict}
plsClasses <- predict(plsFit, newdata = testing)
confusionMatrix(data = plsClasses, testing$Class)
```

### LogicReg

A package for logic regression

```{r LogicReg}
library(LogicReg)
data(logreg.savefit1,logreg.savefit2,logreg.savefit3,logreg.savefit4,
logreg.savefit5,logreg.savefit6,logreg.savefit7,logreg.testdat)
myanneal <- logreg.anneal.control(start = -1, end = -4, iter = 500, update = 100)
fit1 <- logreg(resp = logreg.testdat[,1], bin=logreg.testdat[, 2:21], type = 2,
select = 1, ntrees = 2, anneal.control = myanneal)
plot(fit1)
```

